Improving \textsl{Gaia} parallaxes with a data-driven model \\ of the color--magnitude diagram

### 2017-06-02 paper/paper.tex
prior figure

>>>>

\subsection{prior}
Using \xd\ and the MML method described in the methods section, we generate our prior shown in Figure \ref{fig:prior}.
This is the \gaia\ + \tmass\ data set deconvolved with it's noise, so compared with the raw data in Figure \ref{fig:data}, this is a tighter distribution. The left panel shows 1.3M samples from the prior distribution, and the right panel shows the underlying gaussian mixture model these samples are drawn from. The main sequence and red giant branch are much tighter, as well as the red clump. We'll come back to more features in the data below, especially those seen in the posterior distribution.
